Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-12 doc/report/msc-report.tex
report: added map-reduce diagram.
* Makefile: now builds with dvips -Ppdf instead of pdflatex.
* TODO: removed map-reduce expand note.
* map-reduce.*: diagram of map-reduce data flow.
* msc-report.tex: included map-reduce diagram.

\noindent Per Andersson and Fredrik M{\"o}llerstrand both study Computer
Science at Chalmers University of Technology in Gothenburg, Sweden. This thesis
is part of their master's degree. The work was performed at Last.fm's
office in London during spring 2009.

The authors would like to especially thank the supervisors---David Sands at
Chalmers and Johan Oskarsson and Martin Dittus at Last.fm---for their help and
support.

Per would like to especially thank Hedvig Kamp for help and guidance with the
thesis and general matters in life.

The authors would also like to thank their respective families and friends, and
the staff at Last.fm for their moral support before, during, and after the
thesis work.

>>>>

\noindent Per Andersson and Fredrik M{\"o}llerstrand both study Computer Science
at Chalmers University of Technology. This report is part of their master thesis
degree. The work was performed at Last.fm's office in London during spring 2009.

The authors would like to specially thank the supervisors---David Sands at
Chalmers and Johan Oskarsson and Martin Dittus at Last.fm---for their help and
support.

The authors would also like to thank the staff at Last.fm and their family and
friends for moral support before, during, and after the thesis work.
